Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-02-07 RET_Hosts.tex

The most common method used to estimate the metallicity of galaxies is to use emission line ratios that have been calibrated using theoretical or empirical models in order to approximate the gas-phase oxygen abundance in the interstellar medium. Due to the low S/N of the spectra in this sample, we are constrained to a subset of these diagnostics by the availability of only a handful of the strongest emission lines, namely \halpha, \hbeta, \OII 3727, \OIII 4959 and 5007, \NII 6548 and 6583, and \SII 6717 and 6731. Furthermore, for each host galaxy only a subset of these lines are detected - for example, \halpha, \NII and \SII are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen lines available, mandating the use of the R23 diagnostic. For hosts at $z<0.3$ we are able to use the \OIII /\NII (O3N2) and \NII /\halpha (N2) line ratios.

For the R23 indicator, we use the calibration of \citet{Pettini2004} (PP04), while for O3N2 and N2, we use the calibration of \citet{Marino2013} (M13) in order to directly compare metallicity with the Pisco CCSN sample. We recalculate the metallicities given in \citet{Kruehler2015} using the M13 calibration.

>>>>

The most common method used to estimate the metallicity of galaxies is to use emission line ratios that have been calibrated using theoretical or empirical models in order to approximate the gas-phase oxygen abundance in the interstellar medium. Due to the low S/N of the spectra in this sample, we are constrained to a subset of these diagnostics by the availability of only a handful of the strongest emission lines, namely \halpha, \hbeta, \OII 3727, \OIII 4959 and 5007, \NII 6548 and 6583, and \SII 6717 and 6731. Furthermore, for each host galaxy only a subset of these lines are detected - for example, \halpha, \NII and \SII are redshifted out of the spectral coverage at $z>0.3$, leaving only the oxygen and \hbeta lines available, mandating the use of the R23 diagnostic. For hosts at $z<0.3$ we are able to use the \OIII /\NII (O3N2), \NII /\halpha (N2), and \SII /\NII (S2N2) line ratios.

Due to the redshift rangeTo begin, we determine a set of indicators for which to calculate abundances for our DES RET sample. For the O3N2 and N2 indicators we use the calibration of \citet{Pettini2004} (PP04), and if \SII is detected we derive an abundance using the S2N2 diagnostic of \citet{Dopita2016}. For the R23 indicator, we use the calibration of \citet{Kobulnicky2004} (KK04). At abundances around $12 + \log mathrm{O/H} \sim 8.4$, the R23 indicator becomes two-tailed, with a low and a high value of metallicity corresponding to a single R23 ratio. In cases where the lines are available, we break this degeneracy by cross-calibrating with the \NII / \OII ratio \citep{Kewley2008}. In the cases where \NII is not available, and there are no other diagnostics that can be used to inform the choice of branch, we use the host galaxy mass to derive a crude metallicity estimate from the MZR of \citet{Kewley2008} based upon the PP04 O3N2 diagnostic. For $12 + \log mathrm{O/H}_{\mathrm{MZR}} < 8.4$ we chose the lower branch, while for higher MZR metallicities we choose the upper branch.

To

We recalculate the metallicities given in \citet{Kruehler2015} using the M13 calibration.
